### 2016-07-11 lineups.Rnw
doubly achieved distance figure

\begin{figure}
\centering
<<echo=FALSE, fig.width=8, fig.height = 8, out.width='.6\\linewidth'>>=
lus_summary_3 <- lus_spread %>% group_by(part, lineupid, param_name) %>%
  summarize(
    data_n = sum(true_model=="M3"),
    data_est = mean(M3[true_model=="M3"]),
    data_sd = sd(M3[true_model=="M3"], na.rm=TRUE),
    data_dist = min(M3[true_model=="M1"]) - data_est,
    lower_qu = sum(data_est < M3[true_model=="M1"])/(n()-1)
  )

p1 <- qplot(data_dist, lower_qu,  data = subset(lus_summary_3, !is.na(lower_qu) & param_name=="number pairs at doubly achieved distance 2")) +
  facet_grid(.~part) +
  xlab("Difference in M3 estimate of data panel and minimum of the null panels") +
  ylab("Ratio of null panels with larger M3 estimate") +
  ggtitle("doubly achieved distance")

#gridExtra::grid.arrange(p1,p2)
p1
@
\caption{\label{fig:lusparms-eff2} }
\end{figure}

>>>>

\begin{figure}
\centering
<<echo=FALSE, fig.width=8, fig.height = 8, out.width='.6\\linewidth', warning=FALSE>>=
lus_summary_3 <- lus_spread %>% group_by(part, lineupid, param_name) %>%
  summarize(
    data_n = sum(true_model=="M3"),
    data_est = mean(M3[true_model=="M3"]),
    data_sd = sd(M3[true_model=="M3"], na.rm=TRUE),
    data_dist = min(M3[true_model=="M1"]) - data_est,
    lower_qu = sum(data_est < M3[true_model=="M1"])/(n()-1)
  )

p1 <- qplot(data_dist, lower_qu,  data = subset(lus_summary_3, !is.na(lower_qu) & param_name=="number pairs at doubly achieved distance 2")) +
  facet_grid(.~part) +
  xlab("Difference in M3 estimate of data panel and minimum of the null panels (M1 nulls)") +
  ylab("Ratio of null panels with larger M3 estimate") +
  ggtitle("doubly achieved distance")

lus_summary_3b <- lus_spread %>% group_by(part, lineupid, param_name) %>%
  summarize(
    data_n = sum(true_model=="M1"),
    data_est = mean(M3[true_model=="M1"]),
    data_sd = sd(M3[true_model=="M1"], na.rm=TRUE),
    data_dist = max(M3[true_model=="M3"]) - data_est,
    upper_qu = sum(data_est > M3[true_model=="M3"])/(n()-1)
  )

p2 <- qplot(data_dist, upper_qu,  data = subset(lus_summary_3b, !is.na(upper_qu) & param_name=="number pairs at doubly achieved distance 2" &
part %in% c("smallfriends-eff2", "smallfriends-eff2-rev"))) +
  facet_grid(.~part) +
  xlab("Difference in M3 estimate of data panel and minimum of the null panels (M3 nulls)") +
  ylab("Ratio of null panels with smaller M3 estimate") +
  ggtitle("doubly achieved distance")

gridExtra::grid.arrange(p1,p2)
#p1
@
\caption{\label{fig:lusparms-eff2} }
\end{figure}
